He Said What Now?!: Predicting Interest in the Term *China Virus* by State

### 2020-05-06 Final-Draft.Rmd
final stuff

```{r}
NR_model
```

@@

>>>>

```{r}
NR_model
```
As we see in here, we see that as the days increase we see our China Virus Interest increasing by 0.9 percent. The percent white showed us that as percent white increases, the median China Virus Interest increases by 1.1%. And if a state is red, it will have -3.2 percentage points less compared to a state that is blue. And finally, interestingly the positive count has no influence on how much the percent white changes.

@@

Also as seen in Model2, we see that our Covid-related variable, positive does not show any effect on how many people look up the term. But political differences such as state color show us that red states tend to have the lowest interest while purple and blue states tend to have the highest interest. This is in par with the statistics that show that democrats tend to have a higher political engagement. Finally, after Trump mentioned "China Virus" the interest of the term saw a significant increase 1.1 per Day closer to when Trump held his press conference.
